Collaborative Visual Analysis with RCloud

### 2015-06-26 paper.tex
fix the title
work on abstract

\title{Collaborative Visual Analysis on the Web with RCloud}
% \title{Integrating Social Visual Analysis and Deployment with RCloud}
% \title{Social Visual Analytics: DevOps for Data Scientists}

@@

%% Uncomment below to include a teaser figure.
\teaser{
  \centering
  \includegraphics[width=.80\linewidth]{fig/teaser/teaser.pdf}
  % \vspace{-.5em}
  \caption{
    An overview of features in RCloud. RCloud supports an environment in which a large number of loosely-related problems in data and visual analytics are solved by a small number of \emph{hackers} and \emph{scripters}. In such a shared environment, \emph{discoverability} is a concern. RCloud supports search, annotation, recommendation, and commenting for all notebooks, and provides an overview where users can \emph{browse} popular and recent analyses. When problems and data sources change frequently, deployment can become very costly; RCloud supports \emph{transparent and automatic} deployment of analyses as web pages and web services, allowing a seamless transition from data exploration work to production web services.
  }
% \vspace{-.5em}
}

>>>>

\title{Collaborative Visual Analysis with RCloud}
% \title{Integrating Social Visual Analysis and Deployment with RCloud}
% \title{Social Visual Analytics: DevOps for Data Scientists}

@@

%% Uncomment below to include a teaser figure.
\teaser{
  \centering
  \includegraphics[width=.80\linewidth]{fig/teaser/teaser.pdf}
  % \vspace{-.5em}
  \caption{
An overview of features in RCloud.
RCloud is an environment in which \emph{hackers} and \emph{scripters}
solve problems in data and visual analytics and create web applications
and services.  It is a shared environment, in which \emph{discoverability} is a concern.
RCloud supports search, annotation, recommendation, and commenting for all notebooks, and provides an overview where users can \emph{browse} popular and recent analyses. When problems and data sources change frequently, deployment can become very costly; RCloud supports \emph{transparent and automatic} deployment of analyses as web pages and web services, allowing a seamless transition from data exploration to production.
  }
% \vspace{-.5em}
}
